Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/4_results.tex
added HP comments

\subsection{Connectomics Benchmark}

@@

\begin{table}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
		FlyEM Vol. 1 & 304 / 15949 & 212 / 4578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17614 & 197 / 4366 & 120 & 19 \\ \hline
	\end{tabular}
}
	\centering
	\label{table:skeletonization}
\end{table}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 146 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
We first evaluate the effectiveness of inference augmentation.
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.

>>>>

@@

\begin{table}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23,506) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 610 / 23,506 & 556 / 4,921 & 214 & 160 \\
		FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
	\end{tabular}
}
	\centering
	\label{table:skeletonization}
\end{table}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
\\~\\
\noindent\textbf{Failure Cases}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 146 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
We first evaluate the effectiveness of inference augmentation.
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{\textit{Failure cases.} The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}
Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
